The problem and promise of scale in animal social multilayer networks

### 2020-02-07 paper/manuscript.Rmd
keyword notes
intro edits

## Keywords
Landscape ecology, Movement ecology, Social network analysis, Space use

@@

Unlike traditional monolayer social networks, multilayer networks explicitly
consider social systems across contexts, including scale-dependent contexts
(Pilosof et al. 2017). Multilayer networks are made up of multiple layers, each
representing different classes of individuals (e.g. male or female), types of
behaviours (e.g. grooming, travelling, or foraging), spatial areas (e.g. local
or regional), or temporal windows (e.g. daily or seasonal) (Kivela et al. 2014;
Porter 2018). Multilayer networks are relatively novel to studies of animal
behaviour (Finn et al. 2019; Silk et al. 2018), although they have been used to
describe multidimensional human social systems, complex transportation networks,
and neural networks (Silk et al. 2018). The role of scale within multilayer
social networks remains unexplored but provides a unique opportunity to develop
novel understanding of variation in the temporal or spatial scales associated
with social systems.

Our study is motivated by behavioural, landscape, and spatial ecology to build a
conceptual and analytical framework for scale-dependent multilayer networks and
we apply this framework to a case study of caribou (*Rangifer tarandus*) in
Newfoundland, Canada [@Peignier_2019]. We use this case study to address two
principal questions associated with scale-dependent multilayer networks. First,
to what degree does the social scale of relationships, spatial scale of
landscapes, and temporal scale of analysis influence our ability to interpret
complex social systems? Second, can variation in social, spatial, and temporal
improve predictions associated with biological differences in seasonal resource
availability and social association? We conclude with perspectives for further
development and application of scale in multilayer networks with respect to
habitat selection and space use <!-- TODO: (REF)-->, individual fitness and
phenotypes (Webber & Vander Wal 2018), and movement ecology and collective
movement (Jolles et al. 2019).

>>>>

## Keywords
<!-- TODO: is this the final list ? -->
Social network analysis, Landscape ecology, Movement ecology, Space use

@@

Unlike traditional monolayer social networks, multilayer networks explicitly
consider social systems across contexts, including scale-dependent contexts
(Pilosof et al. 2017). Multilayer networks are made up of multiple layers, each
representing (i) different classes of individuals, e.g. male or female; (ii) types of behaviours, e.g. grooming, travelling, or foraging; and (iii) spatial areas, e.g. local or regional, or temporal windows, e.g. daily or seasonal  (Kivela et al. 2014;
Porter 2018). Multilayer networks are relatively novel to studies of animal
behaviour (Finn et al. 2019; Silk et al. 2018), although they have been used to
describe multidimensional human social systems, complex transportation networks,
and neural networks (Silk et al. 2018). The role of scale within multilayer
social networks remains unexplored but provides a unique opportunity to develop
novel understanding of variation in the temporal or spatial scales associated
with social systems.

Our study is motivated by behavioural, landscape, and spatial ecology to build a
conceptual and analytical framework for scale-dependent multilayer networks and
we apply this framework to a case study of caribou (*Rangifer tarandus*) in
Newfoundland, Canada [@Peignier_2019]. We use this case study to address two
principal questions associated with scale-dependent multilayer networks. First,
to what degree does the social scale of relationships, spatial scale of
landscapes, and temporal scale of analysis influence our ability to interpret
complex social systems? Second, can variation in the social, spatial, and temporal
improve predictions associated with biological differences in seasonal resource
availability and social association? We conclude with perspectives for further
development and application of scale in multilayer networks with respect to phenotypes and individual fitness (Webber & Vander Wal 2018), movement ecology and collective
movement (Jolles et al. 2019), and habitat selection and space use <!-- TODO: (REF)-->,  and .
